---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
bibliography: sfhea.bib
header-includes:
  -  \usepackage{hyperref}
biblio-style: apsr
title: "Application for..."
author:
- name: Darya Vanichkina
- affiliation: University of Sydney
abstract: "This document provides an introduction to R Markdown, argues for its benefits, and presents a sample manuscript template intended for an academic audience. I include basic syntax to R Markdown and a minimal working example of how the analysis itself can be conducted within R with the `knitr` package."
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
# spacing: double
endnote: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE,
                      message=FALSE, warning=FALSE,
                      fig.path='figs/',
                      cache.path = '_cache/',
                      fig.process = function(x) {
                      x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
                      if (file.rename(x, x2)) x2 else x
                      })
library(lemon)
knit_print.data.frame <- lemon_print
```


# Introduction

Academic workflow, certainly in political science, is at a crossroads. 



Almost forgot about creating a footnote.[^1] This will do it again.[^2]

[^1]: The first footnote
[^2]: The second footnote

Want to cite something? 

- Find your biblatexkey in your bib file.
- Put an @ before it, like @smith1984, or whatever it is.
- @smith1984 creates an in-text citation (e.g. Smith (1984) says...)
- [@smith1984] creates a parenthetical citation (Smith, 1984)

That'll also automatically create a reference list at the end of the document.


```{r, fig.cap="A Coefficient Plot", message=F, warning=F,render=lemon_print}


head(mtcars)

```




<!--
# References
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\vspace*{-0.2in}
\noindent
-->
